---
title: "Anshu Uppal's resume"
author: Anshu Uppal
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: 
      - css/custom_resume.css
      - css/styles.css
      - resume
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)

# ======================================================================
# These variables determine how the the data is loaded and how the exports are
# done.

# Is data stored in google sheets? If no data will be gather from the csvs/
# folder in project
using_googlesheets <- FALSE

# Just the copied URL from the sheet
positions_sheet_loc <- "https://docs.google.com/spreadsheets/d/14MQICF2F8-vf8CKPF1m4lyGKO6_thG-4aSwat1e2TWc"

# Is this sheet available for anyone to read? If you're using a private sheet
# set this to false and go to gather_data.R and run the data loading manually
# once to cache authentication
sheet_is_publicly_readable <- TRUE

# Is the goal of this knit to build a document that is exported to PDF? If so
# set this to true to have links turned into footnotes at the end of the
# document
PDF_EXPORT <- FALSE


# A global (gasp) variable that holds all the links that were inserted for
# placement at the end
links <- c()

# ======================================================================
# Now we source two external scripts. One contains functions for building the
# text output and the other loads up our data from either googlesheets or csvs

# Functions for building sections from CSV data
source('parsing_functions.R') 

# Load data for CV/Resume
source('gather_data.R')

# Now we just need to filter down the position data to include less verbose
# categories and only the entries we have designated for the resume
position_data <- position_data %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions', 
      section %in% c('data_science_writings', 'by_me_press') ~ 'writings',
      TRUE ~ section
    )
  ) 
```



Aside
================================================================================


![Anshu Uppal](https://lh3.googleusercontent.com/pw/AJFCJaV2K_mJXRCn9hTjM7hgQsN1che9gUDg_K9raJfyhFtg0q-8uOu7yhsynPbt0PJfASptZBc0IKS6UMmt4omsjOeP_ZjBhd-Ym2vm6LbAtIrtdKJSyGs3CcJtFukT6xx202iw1FNpTU7TeXXawMcAkn1YeEijgA26iwE5HL-vKRdQWrpwG90Fzb6uZc0xZNxyzm7j884_CxYXUFUELsoj3Tai2g035IYyuica6UC3c6EoKkD9xg-om8cJRZV2O2fbUOGOQ8j7Z0dIckK0OksAqECnPw6UhpiDUcayNytEvueyepgszZU2FF31a0MrJR3ScA_0EGT1HzUINefXMOVtvT4f0RY_c1vCsywnPXl657STU_CK9ezQdcXckS9tkNeSxKECcrgEhJegNik8ePSES9n2pPKUUEPUeJL-64SnvkKUO008s2a5xNOMiDOl1GNgjQXlX_WGs_2ohHJg9wAgt2zwp4w7m3sKP7APg69Vf6C2Hl741NmFYsVzE47970BmPtb3bT3SZsc1R9Csf9FyOyNxzgdwgHdXsJe3NV6PP3KscTZgZLQuU5bHK7_ycGTfvaKcJh5wUj3GxcAGIUkbTbvw1HWPXpac9Dh5JH3L0MGHw1_fATarmUyfWXCi6fqgXSMnmevqWzfSXWYifVcSxE5ShJkk8F8T96bFAWMnhRAvaBJp7bPIkdumaiehRO7mAs8a92AJ6SliuzyBJFAjAJKPoqzhktDuwIiMqhKuHl-UuGG83ZJTwmDgxzkt1etM87n0bbH4pdNZPNNl4nWR11HPwdbTPwaKPa7rGeHGRQfu2aiDag-3cG2SYmB7p3SVU4qxZl-r9rrAHUcaJZ--PFNYYc9ticVTnn0dH4v1dUHAAMPRIfgzqCf8ZX3Q9S6Qh3GHFPm3Xb2zLEB2hXXMfl4=w1106-h1106-s-no?authuser=0){width=100%}


Contact Info {#contact}
--------------------------------------------------------------------------------

```{r}
contact_info %>% 
  glue_data("- <i class='fa fa-{icon}'></i> {contact}")
```

Languages {#language_skills}
--------------------------------------------------------------------------------
```{r}
build_skill_bars(language_skills)
```
Skills {#language_skills}
--------------------------------------------------------------------------------
```{r}
build_skill_bars(skills)
```  
  
  
Experienced in statistical analysis, statistical learning models, and optimization methods.

Full experience with next generation sequencing data analysis.

Interests {#skills}
--------------------------------------------------------------------------------
Ultimate frisbee, hiking, reading, Dungeons & Dragons

Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

This CV was made with the R package [**pagedown**](https://github.com/rstudio/pagedown).

Last updated on `r Sys.Date()`.



Main
================================================================================

Anshu Uppal {#title}
--------------------------------------------------------------------------------

### Currently searching for a PhD student position

```{r}
print_text_block(text_blocks, 'intro')
```


Education {data-icon=graduation-cap}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```


<!-- Research Experience {data-icon=laptop} -->
<!-- -------------------------------------------------------------------------------- -->

<!-- ```{r} -->
<!-- position_data %>% print_section('research') -->
<!-- ``` -->


Experience {data-icon=suitcase}
--------------------------------------------------------------------------------


```{r}
position_data %>% print_section('industry')
```


Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------

### Introduction to R Language for Beginners.

Instructor of R and Data Mining Training Courses at SupStat Inc.

Beijing, China

2014

### Computational Biology and Bioinformatics.

Teaching assistant of GBS CB2-201 courses at UAB

AL, USA

2016 - 2017


Selected Publications {data-icon=file}
--------------------------------------------------------------------------------

### No additive genetic variance for tolerance to ethynylestradiol exposure in natural populations of brown trout (Salmo trutta)

*Evolutionary Applications* 12: 940–950

N/A

2019

Marques da Cunha L, ***Uppal A***, Seddon E, Nusbaumer D, Vermeirssen E, Wedekind C

### Sex differentiation in grayling (Salmonidae) goes through an all-male stage and is delayed in genetic males who instead grow faster

*Scientific Reports* 7

N/A

2017

Maitre D, Selmoni OM, ***Uppal A***, Marques da Cunha L, Wilkins LGE, Roux J, et al.

### Genetic correlations and little genetic variance for reaction norms may limit potential for adaptation to pollution by ionic and nanoparticulate silver in a whitefish (Salmonidae)

*Ecology and Evolution* 6: 2751–2762

N/A

2016

Clark ES, Pompini M, ***Uppal A***, Wedekind C